### 2018-08-02 article.tex
Typo + Rewriting systems as 2-PROPS: Definition / Proposition 1

\begin{itemize}
\item a 2-bifunctor $\otimes: \catC \times \catC \to \catC$ such that on 2-cells $r, s, t, u$
$$
(r \otimes s) \circ (t \otimes u) = (r \circ t) \otimes (s \circ u)
$$
\end{itemize}

\begin{remark}[Interchange law]
Because $\circ$ and $\otimes$ are bifunctor, for all 0-cells $a, b \in \catC$ and all 2-cells $r, s, t, u \in \catC(a, b)$

@@

such that for all object $a$
$$
e \succeq \catE(a, a)
$$
for all objects (a, b, c)
$$
\catE(b, c) \oplus \catE(a, b) \succeq \catE(a, c)
$$

@@

$(E, \otimes)$ is strictly monoidal if
$$
\catE(a, b) \oplus \catE(a', b') \succeq \catE(a \otimes a', b \otimes b')
$$
and symmetric if
$$
e \succeq \catE(a \otimes b, b \otimes a)
$$

@@

>>>>

\begin{itemize}
\item a 2-bifunctor $\otimes: \catC \times \catC \to \catC$ such that on 2-cells $r, s, t, u$
\[
(r \otimes s) \circ (t \otimes u) = (r \circ t) \otimes (s \circ u)
\]
\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%        INTERCHANGE LAW REMARK        %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{remark}[Interchange law]
Because $\circ$ and $\otimes$ are bifunctor, for all 0-cells $a, b \in \catC$ and all 2-cells $r, s, t, u \in \catC(a, b)$

@@

such that for all object $a$
\[
e \succeq \catE(a, a)
\]
for all objects (a, b, c)
\[
\catE(b, c) \oplus \catE(a, b) \succeq \catE(a, c)
\]

@@

$(E, \otimes)$ is strictly monoidal if
\[
\catE(a, b) \oplus \catE(a', b') \succeq \catE(a \otimes a', b \otimes b')
\]
and symmetric if
\[
e \succeq \catE(a \otimes b, b \otimes a)
\]

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%        REWRITING SYSTEM        %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
A \emph{groupoid} is a category where morphisms are invertible.
Let's define the following strict monoidal 2-groupoid \catC

\begin{itemize}
\item 0-cells are natural number $\mathbb{N}$
\item 1-cells are quantum circuits freely generated by $\circ$, $\otimes$ and $\{f_i\}_i$, a set of quantum circuits
\item 2-cells are quantum circuit transformations freely generated by $\circ$, $\otimes$ and $\{r_i\}_i$, a set of ransformations, such that $\forall r: f \Rightarrow g \in \{r_i\}_i, \exists r^{-1}: g \Rightarrow f \in \{r_i\}_i$
\[
r \circ r^{-1} = id_f
\]
\item the vertical composition is the usual transformations composition
\item the horizontal composition is the usual circuits composition
\item the 2-bifunctor is
\begin{itemize}
\item on 0-cell, $a \otimes b = a + b$
\item on $\catC(a, b)$, a functor $C(a, b) \otimes C(a', b') \to C(a + a', b + b')$
\end{itemize}
\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%        REWRITING SYSTEM PROPOSITION 1        %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{proposition}
For all transformation $r: f \Rightarrow g$, $r$ can be writen
\[
r = r_1 \bullet r_2 \bullet r_3 \bullet \cdots \bullet r_i
\]

\begin{proof}
We'll prove it by induction of the size of the transformation using the properties of the bifunctors.
With a single transformation, we already have
\[
r = r_1
\]
For the inductive step let's assume $r$ is
\[
r = r_1 \bullet r_2 \bullet r_3 \bullet \cdots \bullet s
\]
If $s$ is such that
\[
s = (s_1 \bullet s_2) \circ (s_3 \bullet s_4)
\]
Then using the interchange law we can write
\[
s = (s_1 \circ s_3) \bullet (s_2 \circ s_4)
\]
So we have 
\begin{align}
r &= r_1 \bullet r_2 \bullet r_3 \bullet \cdots \bullet (s_1 \circ s_3) \bullet (s_2 \circ s_4) \cr
r &= r_1 \bullet r_2 \bullet r_3 \bullet \cdots \bullet r_{i - 1} \bullet r_i
\end{align}
Otherwise we can always add an identity transformation to get the interchange law.
\begin{align}
s_1 \circ (s_3 \bullet s_4) &\Rightarrow (s_1 \bullet id) \circ (s_2 \bullet s_3) \cr
(s_1 \bullet s_2) \circ s_3 &\Rightarrow (s_1 \bullet s_2) \circ (id \bullet s_3)
\end{align}
The same is true with
\[
s = (s_1 \bullet s_2) \otimes (s_3 \bullet s_4)
\]
\end{proof}
\end{proposition}
